Quantum-assisted unsupervised data clustering

### 2020-05-06 manuscript.tex
Keep single figure with Ham dist See #8.

%%%%%
\begin{figure}[t]
	\includegraphics[width=0.95\columnwidth]{distance_matrix.png}
	\caption{
		(a) Hamming distance matrix between two data sets of binary vectors. 
		Values of distance that are less than the median distance value are marked black. 
		Classical simulation of the quantum circuit shows perfect agreement to theoretical calculations. 
		(b) Result obtained on the IBM Q Experience ``ibmq\_16\_melbourne'' backend. 
		We can see good agreement between the distance matrices calculated classically and on the IBM Q Experience.  
	}
	\label{fig:distance_matrix}
\end{figure}
%%%%%

@@

Currently available quantum platforms are still subject to substantial level of noise and extracting the exact distance from amplitude is still a difficult task.
Fortunately, for most of algorithms, SOFM included, the information of nearest vectors is sufficient.

>>>>

%%%%%
\begin{figure}[t]
	\includegraphics[width=0.95\columnwidth]{distance_matrix.eps}
	\caption{
		Hamming distance matrix between two data sets of binary vectors calculated on the IBM Q Experience. 
		Since the information of closest vectors is sufficient values of distance that are less than 1.5 are marked black. 
		Errors caused by noise in comparison with theoretical calulation are marked red cross.
		Result obtained on the IBM Q Experience ``ibmq\_16\_meleourne'' backend. 
		Fidelity of final state~(\ref{eq:final_state}) measurement is 0.8.
	}
	\label{fig:distance_matrix}
\end{figure}
%%%%%

@@

Currently available quantum platforms are still subject to substantial level of noise and extracting the exact distance from amplitude is still a difficult task.
Fortunately, for most of algorithms, SOFM included, the information of nearest vectors is sufficient 
and can be obtained with high fidelity~(Fig.~\ref{fig:distance_matrix}).
